Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex

One tunnel is defined by the exit point and by the active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed simply by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (the exit point at frame $i$) and the active site $\qinit^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p$ to the first active site reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

There are two possible reasons why the active site of the same frame cannot be reached.
First, the exit point is not connected with the same component of the graph as the active site.
Second, the active site does not exist in the given frame, which may happen if large probes are considered.

>>>>

One tunnel is defined by the exit point and by the active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (the exit point at frame $i$) and the active site $\qinit \in \CF^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p \in P^i$ to the first active site $\qinit\in\CF^j, j < i$ reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

%There are two possible reasons why the active site of the same frame cannot be reached.
%First, the exit point is not connected with the same component of the graph as the active site.
%Second, the active site does not exist in the given frame, which may happen if large probes are considered.
